withmice

### 2024-03-01 withmice.Rmd
trying mice on demographic variables and DVs

@@

module2mice <- codedmodule2 %>%
              dplyr::select(starts_with (c("Risky_Nuclear", "Risky_Solar", "Risky_Coal", "Ben_Nuclear", "Ben_Solar", "Ben_Coal","K_S","K_E","DISPLACE", "POLLUTE", "HEALTH", "JOBS", "BEAUTY", "PRIDE", "NPRIDE","DEVNUCLEAR", "DEVSOLAR", "DEVCOAL","PROSPER", "RELY","K_H","K_I", "WEALTHLIM", "MECHANISATION", "DECISIONDECEN", "INDUSTRYSMALL", "ECONOMYLOCAL", "ENVOVERDEV", "OWNERPUB","OWNERREG", "DECISIONCEN", "INDUSTRYLARGE", "ECONOMYGLOBAL", "OWNERPVT", "OWNERNOREG", "DEVOVERENV", "age", "urban_rural", "gender", "caste", "religion", "State"))) %>%
              dplyr::select(!religiontext)

@@

@@

d.pattern(module2mice2)

>>>>

```{r}
## checking correlation with NA

nuclearrel <- codedmodule2 %>%
  dplyr::select(starts_with (c("Risky_Nuclear","Ben_Nuclear","DISPLACENUCLEAR", "POLLUTENUCLEAR","HEALTHNUCLEAR","JOBSNUCLEAR","BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "K_H","K_I", "WEALTHLIM", "MECHANISATION", "DECISIONDECEN", "INDUSTRYSMALL", "ECONOMYLOCAL", "ENVOVERDEV", "OWNERPUB","OWNERREG", "DECISIONCEN", "INDUSTRYLARGE", "ECONOMYGLOBAL", "OWNERPVT", "OWNERNOREG", "DEVOVERENV", "age", "urban_rural", "gender", "caste", "religion", "State")))%>%
              dplyr::select(!religiontext) %>%
              filter(!is.na(gender))

# Store results in a data frame
results <- data.frame(Variable = character(), Correlation = numeric(), P_Value = numeric(), stringsAsFactors = FALSE)

# Loop through all columns in the dataframe
for(var in names(nuclearrel)) {
  # Skip if the variable is not numeric or if it's the same as Risky_Nuclear
  if(!is.numeric(nuclearrel[[var]]) || var == "Risky_Nuclear") next

  # Perform correlation test
  test_result <- cor.test(nuclearrel$Risky_Nuclear, nuclearrel[[var]], use = "complete.obs")

  # Store results
  results <- rbind(results, data.frame(Variable = var, Correlation = test_result$estimate, P_Value = test_result$p.value))
}

# Print the results
print(results)

@@

module2mice <- codedmodule2 %>%
              dplyr::select(starts_with (c("Risky_Nuclear","Ben_Nuclear","DISPLACENUCLEAR", "POLLUTENUCLEAR","HEALTHNUCLEAR","JOBSNUCLEAR","BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Risky_Solar", "Risky_Coal",  "Ben_Solar", "Ben_Coal","K_S","K_E","DISPLACESOLAR","DISPLACESOLARCOAL", "POLLUTESOLAR","POLLUTECOAL",  "HEALTHSOLAR", "HEALTHCOAL",  "JOBSSOLAR", "JOBSCOAL",  "BEAUTYSOLAR", "BEAUTYCOAL",  "PRIDESOLAR", "PRIDECOAL",  "NPRIDESOLAR", "NPRIDECOAL", "DEVSOLAR", "DEVCOAL","PROSPERSOLAR","PROSPERCOAL",  "RELYSOLAR", "RELYCOAL","K_H","K_I", "WEALTHLIM", "MECHANISATION", "DECISIONDECEN", "INDUSTRYSMALL", "ECONOMYLOCAL", "ENVOVERDEV", "OWNERPUB","OWNERREG", "DECISIONCEN", "INDUSTRYLARGE", "ECONOMYGLOBAL", "OWNERPVT", "OWNERNOREG", "DEVOVERENV", "age", "urban_rural", "gender", "caste", "religion", "State"))) %>%
              dplyr::select(!religiontext) %>%
              mutate_all(~ifelse(. == "Other (Please mention)", "Other", .))%>%
              mutate_all(~ifelse(. == "(Other)", "Other", .))%>%
              filter(!is.na(gender))

module2mice$caste[module2mice$caste == "Rather not say/Don't know"] <- NA
module2mice$religion[module2mice$religion == "(Other)"] <- NA

@@

# Identify rows with any NA values
rows_with_na <- apply(module2mice2, 1, function(x) any(is.na(x)))

# View rows that contain NAs
module2mice2[rows_with_na, ]

@@

summary(module2mice2)

mice::md.pattern(module2mice2)

md.pairs(module2mice2)

# predictors - K_EDISCRIM K_ERADEQ1  K_EWEALTH  K_ERADEQ2  age      urban_rural    gender   caste  religion   State  WEALTHLIM  MECHANISATION WEALTHLIM INDUSTRYSMALL INDUSTRYLARGE - these were chosed on the basis of least amount of NAs.

Risky <- module2mice2 %>%
        dplyr::select(starts_with(c("Risky","Ben", "State")))

K <- module2mice2 %>%
        dplyr::select(starts_with(c("K_", "State")))

mice::md.pattern(Risky)

md.pairs(Risky)

K_all <- mice::md.pattern(K)

options(max.print=1000)
K_all

md.pairs(K)
```

```{r, echo = FALSE}

# doing mice with just the DVs and the demographic variables

imp <- mice(module2mice2, maxit = 0)

pred <- imp$predictorMatrix
pred[, c("Risky_Nuclear","Ben_Nuclear", "DISPLACENUCLEAR", "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "HEALTHCOAL","JOBSSOLAR",  "JOBSCOAL", "BEAUTYCOAL",  "PRIDECOAL",  "NPRIDECOAL",  "DEVCOAL", "PROSPERCOAL", "RELYCOAL", "K_HREVDIS1", "Risky_Coal",  "Ben_Coal",  "DISPLACESOLAR",  "BEAUTYSOLAR",  "PROSPERSOLAR",  "RELYSOLAR", "DECISIONDECEN", "ECONOMYLOCAL", "ENVOVERDEV", "OWNERPUB", "DECISIONCEN", "OWNERNOREG", "K_SLIMCHOI", "K_SPROTECT", "POLLUTESOLAR","HEALTHSOLAR", "PRIDESOLAR", "NPRIDESOLAR", "DEVSOLAR","K_HEQUAL", "K_IINTRFER", "K_IPRIVACY", "K_IPROTECT", "OWNERREG", "ECONOMYGLOBAL", "OWNERPVT", "DEVOVERENV" )] <- 0

# Initialize method_list with "" to skip imputation for all variables initially
method_list <- rep("", ncol(module2mice2))
names(method_list) <- colnames(module2mice2)

# Specify the imputation method for variables you want to impute

method_list[c("Risky_Nuclear","Risky_Solar", "Risky_Coal", "Ben_Nuclear", "Ben_Solar", "Ben_Coal", "K_EDISCRIM", "K_ERADEQ1", "K_EWEALTH", "K_ERADEQ2", "WEALTHLIM", "MECHANISATION", "INDUSTRYSMALL", "INDUSTRYLARGE")] <- "polr"
method_list["caste"] <- "polyreg"

imp <- mice(module2mice2, method = method_list, pred = pred, maxit = 15, seed = 123)

print(imp)

imp$imp$caste
